Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere

### 2020-12-08 paper/dcpo_gender_roles.Rmd
fuss with fn re construct vs external convergent validation

In Figure&nbsp;\ref{surv_const_plot}, we move on to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
For purposes of construct validation, we turn first to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
Although many of the items in this category are on their face at best only very tangentially related to public gender egalitarianism, others are plausibly causally related.
Consider `wantch4`, an item asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children."
As agreement suggests that women do not truly care about opportunities in the workplace, those who do should be expected to be less likely to believe women should enjoy equal access to such opportunities which men implicitly value more.
Or, similarly, `familywoman4`, an item from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family." 
Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
Indeed, the `tradroles` family of questions, which couple the `familywoman` stem with the idea that the most important role of a man is to earn money---and so more explicitly indicates that the public sphere is appropriately segregated by gender---is included among the items used to estimate the PGE data.
If these two questions are thought of as indicators of public gender egalitarianism, then, because they are not included in the PGE source data, these plots constitute not construct validation but rather "external" convergent validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
In either case, they provide evidence of the validity of the PGE Mean scores.]
In a slightly different vein, 
With regard to both the internal and external items, the correlations are negative (as expected given the polarity of these questions) and are very strong.

>>>>

In Figure&nbsp;\ref{surv_const_plot}, we move on to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
For purposes of construct validation, we turn first to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
Although many of the items in this category are on their face at best only very tangentially related to public gender egalitarianism, others are plausibly causally related.
Consider `wantch4`, an item asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children."
As agreement suggests that women do not truly care about opportunities in the workplace, those who do should be expected to be less likely to believe women should enjoy equal access to such opportunities which men implicitly value more.
Or, similarly, `familywoman4`, an item from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family." 
Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
(Indeed, the `tradroles` series of questions, which couple the `familywoman4` stem with the idea that the most important role of a man is to earn money---and so more explicitly indicates that the public sphere is appropriately segregated by gender---is included among the items used to estimate the PGE data.)
If these two questions are thought of as indicators of public gender egalitarianism, then, because they are not included in the PGE source data, these plots constitute not construct validation but rather "external" convergent validation [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
In either case, though, they provide evidence of the validity of the PGE Mean scores.]
In a slightly different vein, 
With regard to both the internal and external items, the correlations are negative (as expected given the polarity of these questions) and are very strong.
